---
title: "Data Cleaning"
author: "He YOU (Libby)"
date: "4/30/2018"
output: html_document
---

```{r}
library(stringr)
library(lubridate)
library(dplyr)
```

```{r}
data = read.csv("311_Service_Requests_2017.csv",na.strings = "")
```

```{r}
str(data)
```

## Add a new column named "Complaint.SubType" with subtypes of complaint subtracted from Complaint.Type
```{r}
data$Complaint.Type = as.character(data$Complaint.Type)
data$Complaint.SubType = str_sub(data$Complaint.Type,start = 9)
data$Complaint.SubType = as.factor(data$Complaint.SubType)
data$Complaint.SubType = str_replace_all(data$Complaint.SubType,"^\\s*$","Others")
data$Complaint.Type = as.factor(data$Complaint.Type)
```


```{r}
data$Created.Date = mdy_hms(data$Created.Date)
data$Closed.Date = mdy_hms(data$Closed.Date)
data$Due.Date = mdy_hms(data$Due.Date)
data$Resolution.Action.Updated.Date = mdy_hms(data$Resolution.Action.Updated.Date)
```

## Add new columns named Created.Month, Created.Weekday, Created.Time and Created.Hour to store the month, day of the week, time and hour of the day for created date of the complaint.

```{r}
data$Created.Month = month(data$Created.Date,label = T, abbr = T)
data$Created.Weekday = wday(data$Created.Date,label = T, abbr = T)
data$Created.Time = str_sub(data$Created.Date,start = 12)
data$Created.Time = hms(data$Created.Time)
data$Created.Hour = hour(data$Created.Date)
```

## Add a new column named Date.Diff to calculate the difference between created date and closed data in seconds.
```{r}
data$Date.Diff_day = difftime(data$Closed.Date,data$Created.Date,units = "days")
```

## Select columns that will be used
```{r}
data = data %>%
  select(-c(Taxi.Company.Borough:Bridge.Highway.Segment,Street.Name:Intersection.Street.2,BBL:Vehicle.Type))
```

```{r}
str(data)
```


## Save the file
```{r}
save(data, file = "data.RData")
```

## Agency Analysis Data Cleaning
```{r}
load("data.RData")
```

## Create a new dataset only dealing with closed cases, since only closed cases have solutions
```{r}
data.agency = data[data$Status=="Closed",]
data.agency$Resolution.Description = as.character(data.agency$Resolution.Description)
```


```{r}
nrow(data.agency[is.na(data.agency$Resolution.Description),])
```
We found that only 9 closed complaints are recorded without a resolution, which is a minimal number. Thus, we only focus on those with a resolution.

```{r}
data.agency=data.agency[!is.na(data.agency$Resolution.Description),]
```

#### Depending on resolution description, we chould see agency's evaluation towards these complaints, among the 41 categories of Resolutions. And we divided them into 3 levels: Level1 - investigation or respond needed; Level2 - could be resolved or closed by referring or contacting; Level3 - respond is unnecessary. Then we create a column named Leve to show which importance level the complaint belongs to.

```{r}
data.agency = data.agency %>%
  mutate(Level = 0)
```


Data cleaning of Level_1
```{r}
level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection attempted to inspect this complaint but[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection attempted to investigate this complaint[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection conducted an inspection and determined[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection determined that an inspection is warranted[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection did not observe a violation[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection has inspected your complaint and determined that further investigation is required[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection investigated this complaint[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection observed a violation[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The New York City Economic Development Corporation determined that the helicopter tour operator was operating within the limits[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department issued a summons[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department made an arrest[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department responded and upon arrival those responsible for[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department responded to the complaint and a report[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department responded to the complaint and took action[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department responded to the complaint and with the information available [.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"The Police Department responded to the complaint but officers were unable to gain entry[.*]?")
data.agency$Level[level_1]="Level_1"

level_1=str_detect(data.agency$Resolution.Description,"Your complaint has been received by the Police Department and it has been determined that a long-term investigation[.*]?")
data.agency$Level[level_1]="Level_1"

```


Data cleaning of Level_2
```{r}
level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection determined that an inspection is not warranted[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection determined that this complaint is not under its jurisdiction and referred[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection received a letter or phone call from the alleged dog owner[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection requires an appointment[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection requires contact with the complainant[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection requires contact with the complainant[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection researched this complaint[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection resolved this complaint[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection scheduled an inspection[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Department of Environmental Protection sent a letter to the complainant[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The New York City Economic Development Corporation received your complaint. You did not provide enough information[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"The Police Department reviewed your complaint and provided additional information[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"Your complaint has been forwarded to the New York Police Department for a non-emergency response[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"Your complaint has been received by the Police Department and additional information[.*]?")
data.agency$Level[level_2]="Level_2"

level_2=str_detect(data.agency$Resolution.Description,"Your complaint has been submitted to the New York City Economic Development Corporation for further investigation[.*]?")
data.agency$Level[level_2]="Level_2"
```

Level_3
```{r}
data.agency$Level[data.agency$Level==0]="level_3"
```

## Export Closed into RData file
```{r}
save(data.agency,file = "Closed.RData")
```

### Complaints with importance level 1

```{r}
data.level1=data.agency[data.agency$Level=="Level_1",]
```


```{r}
data.level1$Problem.Solution=0
```

### whether a level1 case has solution

For Level1 cases, some has specific resolution, but some are not given an actual resolution. Thus, we create a column called Resolution.Description
```{r}
No=str_detect(data.level1$Resolution.Description,"The Department of Environmental Protection attempted to inspect this complaint but[.*]?")
data.level1$Problem.Solution[No]="No"

No=str_detect(data.level1$Resolution.Description,"The Department of Environmental Protection attempted to investigate[.*]?")
data.level1$Problem.Solution[No]="No"

No=str_detect(data.level1$Resolution.Description,"The Police Department responded to the complaint but[.*]?")
data.level1$Problem.Solution[No]="No"
```

```{r}
data.level1$Problem.Solution[data.level1$Problem.Solution==0]="Yes"
```

### Results
Add a column "Result/Details", if there is a solution to the complaint, then show the specific results; if there is no solution to the complain, will show the reason why the investigation doesn't work.

```{r}
data.level1$Result.Detail=0
```

## Reasons for no results:

```{r}
No=str_detect(data.level1$Resolution.Description,"[.*]?gain[.*]?")
data.level1$Result.Detail[No]="Entry unobtainable"

No=str_detect(data.level1$Resolution.Description,"[.*]?address was incorrect[.*]?")
data.level1$Result.Detail[No]="Incorrect address"
```


## Resolution for with results
```{r}
Yes=str_detect(data.level1$Resolution.Description,"[.*]?did not observe a violation[.*]?")
data.level1$Result.Detail[Yes]="No evidence of violation"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?operating within the limits[.*]?")
data.level1$Result.Detail[Yes]="No evidence of violation"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?no evidence of the violation[.*]?")
data.level1$Result.Detail[Yes]="No evidence of violation"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?responsible for the condition were gone[.*]?")
data.level1$Result.Detail[Yes]="No evidence of violation"


Yes=str_detect(data.level1$Resolution.Description,"[.*]?observed a violation[.*]?")
data.level1$Result.Detail[Yes]="Violation resolved"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?in response to the complaint[.*]?")
data.level1$Result.Detail[Yes]="Violation resolved"


Yes=str_detect(data.level1$Resolution.Description,"[.*]?signs are not warranted[.*]?")
data.level1$Result.Detail[Yes]="Condition fixed"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?shut the running hydrant[.*]?")
data.level1$Result.Detail[Yes]="Condition fixed"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?report was prepared[.*]?")
data.level1$Result.Detail[Yes]="Condition fixed"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?took action to fix the condition[.*]?")
data.level1$Result.Detail[Yes]="Condition fixed"


Yes=str_detect(data.level1$Resolution.Description,"[.*]?inspection is warranted to investigate[.*]?")
data.level1$Result.Detail[Yes]="Further investigation"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?further investigation[.*]?")
data.level1$Result.Detail[Yes]="Further investigation"

Yes=str_detect(data.level1$Resolution.Description,"[.*]?long-term investigation[.*]?")
data.level1$Result.Detail[Yes]="Further investigation"


Yes=str_detect(data.level1$Resolution.Description,"[.*]?referred[.*]?")
data.level1$Result.Detail[Yes]="Referred"

```


```{r}
data.level1 = data.level1 %>%
  select(Unique.Key,Created.Date, Closed.Date,Agency, Complaint.Type, Descriptor,Status, Resolution.Description,Resolution.Action.Updated.Date, Latitude, Longitude,Complaint.SubType, Created.Month,Created.Weekday, Created.Time, Created.Hour, Date.Diff_day, Level,Problem.Solution, Result.Detail)
```


```{r}
data.level1$Level = as.factor(data.level1$Level)
data.level1$Problem.Solution = as.factor(data.level1$Problem.Solution)
data.level1$Result.Detail = as.factor(data.level1$Result.Detail)
```


### Exporting to csv
```{r}
save(data.level1,file = "level1.RData")

```